Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-09-11 tex/MesnardoBarba2019.tex
add author bios

>>>>

\textbf{Olivier Mesnard} is a doctoral student at the George Washington University. His research interests include computational fluid dynamics and immersed boundary methods with application to animal locomotion. Mesnard has an Engineering degree from Institut Sup{\'e}rieur de M{\'e}canique de Paris and an MS from Universit{\'e} Pierre et Marie Curie. Contact him at mesnardo@gwu.edu.

\textbf{Lorena A. Barba} is a professor of mechanical and aerospace engineering at the George Washington University. Her research interests include computational fluid dynamics, biophysics, and high-performance computing. She is co-Editor of the CiSE Reproducible Research Track, Associate Editor for The ReScience Journal, Associate Editor-in-Chief of the Journal of Open Source Software, and Editor-in-Chief of the Journal of Open Source Education. Barba received a PhD in aeronautics from the California Institute of Technology. Contact her at labarba@gwu.edu.
